---
title: "Test Report"
author: "Hamish McWilliam"
date: "4 June 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r db_connect}
# SQLite database filename
dbFilename <- 'C:/VBox_share/NAS.sqlite'

# Open a connection to the SQLite database
library(DBI)
dbConn = dbConnect(drv=RSQLite::SQLite(), dbname=dbFilename)
```

## Basic Filesystem Information

Total number of files:
```{r totalNumberOfFiles}
totalNumberOfFiles <- dbGetQuery(dbConn, 'SELECT COUNT(fullFilename) FROM files;')
print(totalNumberOfFiles)
```

Total number of directories:
```
# TODO: requires directory information to be added to database
```

Total file size:
```{r fileSizes}
# Cast required to avoid issues with number truncation due to use of 32-bit integers.
fileSizes <- dbGetQuery(dbConn, 'SELECT cast(sizeKb AS TEXT) FROM files;')
fileSizes['sizeKb'] <- as.numeric(fileSizes[,'cast(sizeKb AS TEXT)']) / 1000

print(sum(fileSizes['sizeKb']))
```

Summary statistics for file sizes:
```{r fileSizes_summary}
print(summary(fileSizes['sizeKb']))
```

Distribution of file sizes:
```{r fileSizes_distribution}
hist(log(fileSizes$sizeKb, 2), freq=TRUE)
```

## File Extensions

Number of unique file extensions:
```{r file_extensions}
fileExtensions <- dbGetQuery(dbConn, 'SELECT fileExtension, COUNT(fileExtension) FROM files GROUP BY fileExtension;')
nrow(fileExtensions)
```

Summary statistics for file extensions:
```{r}
summary(fileExtensions$`COUNT(fileExtension)`)
```

```{r}
# TODO histogram of file extension frequencies.
hist(log(fileExtensions$`COUNT(fileExtension)`, 10), freq=TRUE)
```

Most common file extensions:
```{r}
fileExtensions_sorted <- fileExtensions[order(fileExtensions$`COUNT(fileExtension)`, decreasing=TRUE),]
( popular_fileExtensions <- head(fileExtensions_sorted, n=10) )
```

## MIME Types

Number of unique MIME types:
```{r mime_types}
mimeTypes = dbGetQuery(dbConn, 'SELECT MIMEType, COUNT(MIMEType) FROM files GROUP BY MIMEType;')
nrow(mimeTypes)
```

```{r}
# TODO histogram of MIME type frequencies
hist(log(mimeTypes$`COUNT(MIMEType)`, 10), freq=TRUE)
```

For the most commonly occurring MIME types determine the cumulative data size:
```{r mime_types_size}
mimeTypes_sorted <- mimeTypes[order(mimeTypes[2], decreasing=TRUE),]
( popular_mimeTypes <- head(mimeTypes_sorted, n=10) )

sizeStats <- function(mimeType) {
  # Map file sizes to numeric to avoid issues with 32-bit integers
  tmpQuery <- paste('SELECT SHA256, cast(sizeKb AS TEXT) FROM files WHERE MIMEType IS \'', mimeType, '\';', sep='')
  tmpResult <- dbGetQuery(dbConn, tmpQuery)
  tmpResult['sizeKb'] <- as.numeric(tmpResult[,'cast(sizeKb AS TEXT)']) / 1000
  
  # All files
  print(nrow(tmpResult))
  print(sum(tmpResult['sizeKb']))
  print(summary(tmpResult['sizeKb']))

  # Unique files
  tmpResult <- unique(tmpResult)
  print(nrow(tmpResult))
  print(sum(tmpResult['sizeKb']))
  print(summary(tmpResult['sizeKb']))
}

for(i in seq(10)) {
  mimeType <- popular_mimeTypes[i, 1]
  print(mimeType)
  sizeStats(mimeType)
}
```

## Checksums/digests

Number of unique files, using each checksum/digest method:
```{r digests}
md5Digests = dbGetQuery(dbConn, 'SELECT MD5, COUNT(MD5) FROM files GROUP BY MD5;')
nrow(md5Digests)
sha256Digests = dbGetQuery(dbConn, 'SELECT SHA256, COUNT(SHA256) FROM files GROUP BY SHA256;')
nrow(sha256Digests)
```

```
# TODO histogram of checksum occurance frequencies
  # Plot the Global Active Power data as a histogram.
  hist(data$Global_active_power, col='red', main='Global Active Power', 
       xlab='Global Active Power (kilowatts)')

```

## Close the database and clean-up

```{r db_disconnect}
# Disconnect from database to free resources
dbDisconnect(dbConn)
```

## TODO

* Media intersction. For example: are all the files on an SD card also on the NAS?
* Distribution of file-types
* Distribution of file extensions
* Distribution of file sizes
* Frequency Distribution of duplication
